PANCHANGE_data_preprocessing

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
I think I fixed the psychosis bit

Psychotic disorders group
```{r glad mhd psychotic_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    psychotic_disorders_numeric =
      case_when(
        mhd.schizophrenia_numeric == "1" ~ 1,
        mhd.schizoaffective_disorder_numeric == "1" ~ 1,
        mhd.type_psychosis_psychotic_illness_numeric == "1" ~ 1,
        (mhd.schizophrenia_numeric == "0" &
        mhd.schizoaffective_disorder_numeric == "0" &
        mhd.type_psychosis_psychotic_illness_numeric == "0") ~ 0
      )
  )

@@

```{r Check psychotic_disorders}
glad.mhd.raw.id %>%
  select(
    psychotic_disorders,
    psychotic_disorders_numeric,
    mhd.schizophrenia_numeric,
    mhd.schizoaffective_disorder_numeric,
    mhd.type_psychosis_psychotic_illness_numeric,
    mhd.schizophrenia,
    mhd.schizoaffective_disorder,
    mhd.type_psychosis_psychotic_illness
  )
```

Overlap between self-report schizophrenia and bipolar disorder
+++CH: Check overlap between schizophrenia group and bipolar disorder
++KT: Only 63 with comorbid self-report bipolar disorder and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
```{r glad mhd bipolar_and_schizophrenia_numeric}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia_numeric =
      case_when(
        psychotic_disorders_numeric == 1 &
          mhd.mania_hypomania_bipolar_or_manicdepression == 1 ~ 0,
        psychotic_disorders_numeric == 1 &
          mhd.mania_hypomania_bipolar_or_manicdepression == 1 ~ 1,
        psychotic_disorders_numeric == 1 &
          mhd.mania_hypomania_bipolar_or_manicdepression == 0 ~ 2,
        psychotic_disorders_numeric == 0 &
          mhd.mania_hypomania_bipolar_or_manicdepression == 1 ~ 3
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia =
      recode_factor(bipolar_and_schizophrenia_numeric,
                    "0" = "No psychotic or bipolar disorder",
                    "1" = "Psychotic and bipolar disorder",
                    "2" = "Only psychotic disorder",
                    "2" = "Only bipolar disorder",
                    missing = NA_character_
                    )
  )

@@

>>>>

Psychotic disorders group
[63] "mhd.schizophrenia_numeric"                                 
[64] "mhd.schizoaffective_disorder_numeric"                      
[65] "mhd.type_psychosis_psychotic_illness_numeric" 
```{r glad mhd psychotic_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    psychotic_disorders_numeric =
      case_when(
        mhd.schizophrenia_numeric == "1" ~ 1,
        mhd.schizoaffective_disorder_numeric == "1" ~ 1,
        mhd.type_psychosis_psychotic_illness_numeric == "1" ~ 1,
        (mhd.schizophrenia_numeric == "0" &
        mhd.schizoaffective_disorder_numeric == "0" &
        mhd.type_psychosis_psychotic_illness_numeric == "0") ~ 0
      )
  )

@@

Overlap between self-report schizophrenia and bipolar disorder
+++CH: Check overlap between schizophrenia group and bipolar disorder
++KT: Only 63 with comorbid self-report bipolar disorder and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
```{r glad mhd bipolar_and_schizophrenia_numeric}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia_numeric =
      case_when(
        psychotic_disorders_numeric == 0 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 0 ~ 0,
                psychotic_disorders_numeric == 1 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 0 ~ 2,
        psychotic_disorders_numeric == 0 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 3,
                psychotic_disorders_numeric == 1 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 1
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia =
      recode_factor(bipolar_and_schizophrenia_numeric,
                    "0" = "No psychotic or bipolar disorder",
                    "1" = "Psychotic and bipolar disorder",
                    "2" = "Only psychotic disorder",
                    "3" = "Only bipolar disorder",
                    missing = NA_character_
                    )
  )

@@

```{r Check psychotic_disorders}
glad.mhd.raw.id %>%
  select(
    psychotic_disorders,
    psychotic_disorders_numeric,
    bipolar_and_schizophrenia,
    bipolar_and_schizophrenia_numeric,
    mhd.schizophrenia_numeric,
    mhd.schizoaffective_disorder_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.type_psychosis_psychotic_illness_numeric,
    mhd.schizophrenia,
    mhd.schizoaffective_disorder,
    mhd.type_psychosis_psychotic_illness
  )
```
